curiobaby_drop OED

### 2020-01-15 analysis/OEDcheck.Rmd

```{r, load-data}
dirs = list.files("agent-data")
d = data.frame()
for(dir in dirs) {
  filenames <- list.files(paste("agent-data",dir,sep='/'), full.names=TRUE)
  for(f in filenames) {
    tmp <- read.csv(f, header=T)
    d = rbind(d, tmp)
  }
}
```

@@

hash_cols <- function(dat, cols) {
  shapes = c("Bowl", "Cylinder", "Cone", "Cube", "Dumbbell", "Octahedron", 
             "Pentagon", "Pipe", "Pyramid", "Ring", "Sphere", "TriangularPrism")
  for(i in 1:length(cols)) {
    dat[,cols[i]] = as.numeric(factor(dat[,cols[i]], levels=shapes)) #* 10^(i-1)
  }
  for(r in 1:nrow(dat)) {
    dat[r,cols] = sort(dat[,cols])
  }
  for(i in 1:length(cols)) {
    dat[,cols[i]] = dat[,cols[i]] * 10^(i-1)
  }
  hash = rowSums(dat[,cols])
  return(hash)
}

@@

df <- d %>% 
  filter(
    !ground_object_1 %in% unwanted,
    !ground_object_2 %in% unwanted,
    !ground_object_3 %in% unwanted,
    !available_drop_object_1 %in% unwanted,
    !available_drop_object_2 %in% unwanted,
    !available_drop_object_3 %in% unwanted
  )

@@

>>>>

```{r, load-data}
dirs = list.files("agent-data")
d = data.frame()
for(dir in dirs) {
  filenames <- list.files(paste("agent-data",dir,sep='/'), full.names=TRUE)
  for(f in filenames) {
    #tmp <- read.csv(f, header=T)
    tmp <- read.table(f, sep=',', header=T, stringsAsFactors = F)
    d = rbind(d, tmp)
  }
}
```

@@

hash_cols <- function(dat, cols) {
  shapes = c("Bowl", "Cylinder", "Cone", "Cube", "Dumbbell", "Octahedron", 
             "Pentagon", "Pipe", "Pyramid", "Ring", "Sphere", "TriangularPrism")
  for(i in 1:length(cols)) {
    dat[,cols[i]] = as.numeric(factor(dat[,cols[i]], levels=shapes)) #* 10^(i-1)
  }
  for(r in 1:nrow(dat)) {
    dat[r,cols] = sort(dat[r,cols])
  }
  for(i in 1:length(cols)) {
    dat[,cols[i]] = dat[,cols[i]] * 10^(i-1)
  }
  hash = rowSums(dat[,cols])
  return(hash)
}

@@

df <- d %>% 
  filter(
    !ground_object_1 %in% unwanted,
    !ground_object_2 %in% unwanted,
    !ground_object_3 %in% unwanted,
    !available_drop_object_1 %in% unwanted,
    !available_drop_object_2 %in% unwanted,
    !available_drop_object_3 %in% unwanted
  ) # 3200 left

@@

A = c("Pyramid", "Torus", "TriangularPrism")
B = c("Cone", "Octahedron", "Pipe")
C = c("Bowl", "Dumbbell", "Pentagon")
d$DropSet = NA
for(r in 1:nrow(d)) {
  model_drop_objs = d[r,paste0("available_drop_object_", 1:3)]
  d[r,]$DropSet = ifelse(setequal(model_drop_objs, A), "A", 
                    ifelse(setequal(model_drop_objs, B), "B",
                      ifelse(setequal(model_drop_objs, C), "C", NA)))
}

xp = na.omit(d)
